Estimating duration in the presence of misclassification

### 2024-01-17 cis-imperfect-testing.tex
deal with (almost all) comments or turn into todos

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$, with a value between 60\% and 80\% reproducing the number of single positive episodes observed in the CIS data (see \cref{imperf-test:fig:sim-single-pos}).
In \cref{E-ATACCC}, I estimated that $\psens$ ($1-\rho$ in \cref{E-ATACCC}'s parameterisation) is 95\% (95\% CrI: 96\%--93\%).
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, means this is a reliable estimate during the period for which the individuals are followed-up.
The requirement for a much lower value of $\psens$ in the simulation study suggests this model of false negatives is inadequate.

@@

When $\psens = 0.8$ and is correctly specified, the model recovers the true survival time well (see \cref{imperf-test:fig:constant-test-sensitivity}(B)).
The informative prior, in comparison to the vague prior, helps to overcome the misspecification due to the simplyifying assumptions, moving the estimated survival function closer to its true survival time.
However, when $\psens = 0.6$, this is no longer the case (see \cref{imperf-test:fig:constant-test-sensitivity}(A)).
This is likely caused by too large a violation of the simplifying assumptions made in \cref{imperf-test:sec:modelling}.
\begin{figure}
  % \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}}
  \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}
  \caption[Simulation study results with constant test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a correctly specified test sensitivity.
    True survival time shown in black.
  }
  \label{imperf-test:fig:constant-test-sensitivity}
\end{figure}

If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates,
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is underestimated.
This affect dominates over the opposing bias of overestimating the number of missed episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    True survival time shown in black.
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence (B) is correctly specified, and the same as in \cref{imperf-test:fig:constant-test-sensitivity}, but (A) and (C) have misspecified $\psens$.
    All results uses the combination prior, due to it performing better than the vague prior in \cref{imperf-test:fig:constant-test-sensitivity}.
  }
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}

>>>>

I modified the simulation study from \cref{E-perf-test:sec:simulation-study} to include the possibility of false negatives.
More single positive episodes are seen at lower values of $\psens$ (see \cref{imperf-test:fig:sim-single-pos}).
A value between 60\% and 80\% for $\psens$ reproduces the number of single positive episodes observed within the CIS data.
In \cref{E-ATACCC}, I estimated that the rate of false negatives is\todo{add what the ATACCC false negative rate is}.
The daily testing in the ATACCC study, used for the \cref{E-ATACCC} estimates, should provide a reliable estimate of the false negative rate during the period for which the individuals are followed-up\todo{rephrase this sentence, currently unclear}.
The requirement for a much lower value of $\psens$ suggests this model of false negatives is inadequate.

@@

When $\psens = 0.8$ and is correctly specified, the model recovers the true survival time well (see \cref{imperf-test:fig:constant-test-sensitivity}(B)).
The informative prior, in comparison to the vague prior, helps to overcome the misspecification due to the simplyifying assumptions, moving the estimated survival function closer to its true survival time.
However, when $\psens = 0.6$, this is no longer the case (see \cref{imperf-test:fig:constant-test-sensitivity}(A)).
This is likely caused by too large a violation of the simplifying assumptions made in \cref{imperf-test:sec:modelling}.
\begin{figure}
  % \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}}
  \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}
  \caption[Simulation study results with constant test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a correctly specified test sensitivity.
    True survival time shown in black.
  }
  \todo[inline]{Label 0.6 sub-plot as (A) and 0.8 as (B). Include psens in the facet labelling.}
  \label{imperf-test:fig:constant-test-sensitivity}
\end{figure}

If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates,
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is underestimated.
This affect dominates over the opposing bias of overestimating the number of missed episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    True survival time shown in black.
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence (B) is correctly specified, and the same as in \cref{imperf-test:fig:constant-test-sensitivity}, but (A) and (C) have misspecified $\psens$.
    All results uses the combination prior, due to it performing better than the vague prior in \cref{imperf-test:fig:constant-test-sensitivity}.
  }
   \todo[inline]{Label sub-plots (A--C). Include psens in the facet labelling.}
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}
